A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-05-19 paper/paper.tex
Clarify in intro that we discuss only the induced variant

This paper considers the \emph{maximum common induced subgraph} problem, in
which the objective is to find a graph with as many vertices as possible which
is an induced subgraph of each of two input graphs.  (The \emph{maximum common
partial subgraph} problem instead asks for a common non-induced subgraph with
as many \emph{edges} as possible \citep{DBLP:conf/cp/NdiayeS11}.) We introduce
a new branch and bound algorithm which exploits special properties of the
problem to allow a much faster exploration of the search space, whilst
retaining the filtering and bounding benefits of the constraint programming
approach. We describe the algorithm for the basic maximum common subgraph
problem, and discuss how it may be adapted to handle vertex labels, edge
labels, and the requirement that the found subgraph be connected. We then
present an empirical study of the algorithm, demonstrating that it improves the
state of the art by more than an order of magnitude on the unlabelled variant
of the problem, and showing that it can handle much larger instances than
earlier constraint programming or clique approaches due to lower memory usage.

>>>>

This paper considers the \emph{maximum common induced subgraph} problem, in
which the objective is to find a graph with as many vertices as possible which
is an induced subgraph of each of two input graphs.  (The \emph{maximum common
partial subgraph} problem instead asks for a common non-induced subgraph with
as many \emph{edges} as possible \citep{DBLP:conf/cp/NdiayeS11}; we discuss
only the induced variant in this paper.) We introduce
a new branch and bound algorithm which exploits special properties of the
problem to allow a much faster exploration of the search space, whilst
retaining the filtering and bounding benefits of the constraint programming
approach. We describe the algorithm for the basic maximum common subgraph
problem, and discuss how it may be adapted to handle vertex labels, edge
labels, and the requirement that the found subgraph be connected. We then
present an empirical study of the algorithm, demonstrating that it improves the
state of the art by more than an order of magnitude on the unlabelled variant
of the problem, and showing that it can handle much larger instances than
earlier constraint programming or clique approaches due to lower memory usage.
